---
title: "Leaflet Interactive Map"
author: "Panayiotis L."
date: "9/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
In this report we will use the leaflet package to create an interactive map, 
using the surface water dataset from the colorado.gov website.

## Load libraries
```{r libraries, message=FALSE, warning=FALSE}
library(data.table)
library(tidyr)
library(dplyr)
library(leaflet) 
library(ggplot2)
library(rjson)
library(jsonlite)
library(RCurl)
```

## Requirements
```{r requirements}
sessionInfo()
```

## About the data
The [Colorado Information Marketplace](https://data.colorado.gov/) is a 
comprehensive data warehouse that contains a wide range of Colorado-specific 
open datasets available via a RESTful API called the Socrata Open Data API 
(SODA). We will use this API to get water stations data for Colorado.

## Getting the data

In order to create an interactive map we need some data with coordinates. In this
report we will use the surface water data along with leaflet. More specifically,
we will:

1. Request and get the data from the colorado.gov SODA API in R using fromJSON().
2. Address column data types to ensure our quantitative data (number values) data 
are in fact numeric.
3. Remove missing values (NAs).

```{r get_data, warning=FALSE}
base_url <- "https://data.colorado.gov/resource/j5pc-4t32.json?"
full_url <- paste0(base_url, "station_status=Active")
water_data <- getURL(URLencode(full_url))

water_data_df <- fromJSON(water_data) %>% 
    flatten(recursive = TRUE)

water_data_df <- water_data_df %>%
    mutate_at(vars(amount, location.latitude, location.longitude), 
              funs(as.numeric)) %>%
    filter(!is.na(location.latitude))
```

## Leaflet Map
Now we can use leaflet to create an interactive map with the water data. We will
use clusters to ensure that our map is simple and clean. We also display the 
water station name for each marker.

```{r create_map}
water_data_df$station_type <- factor(water_data_df$station_type)

unique_markers_map <- leaflet(water_data_df) %>%
    addTiles() %>%
        addMarkers(clusterOptions = markerClusterOptions(), 
                   lng=~location.longitude, lat=~location.latitude,
                   popup=~station_name, label=~as.character(station_name))

unique_markers_map
```

## Conclusion
Using Leaflet we can easily generate a map with geo-spatial data. In our case 
it was a map with the water stations of Colorado. 


