---
title: "Plotly Presentation"
author: "Panayiotis L."
date: "9/26/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
In this presentation we will use the plotly package to create several 
interactive plots, using the "mpg" dataset. 

Plotly can also be used with ggplot2 to create more advanced plots, however, 
in this presentation we will cover only a few basic plots.

## Load libraries
```{r libraries, message=FALSE, warning=FALSE}
library(data.table)
library(tidyr)
library(dplyr)
library(plotly)
```

## Requirements
```{r info, comment="", echo=FALSE}
sessionInfo()
```

## Load mpg data

```{r data, comment=""}
data("mpg")
str(mpg)
```

## Create Boxplot
```{r boxplot, warning=FALSE, message=FALSE}
plot_ly(x=as.factor(mpg$cyl), y=mpg$hwy, type="box", color=as.factor(mpg$cyl))
```

## Create 2d scatterplot
```{r scatterplot, warning=FALSE, message=FALSE}
plot_ly(x=mpg$cty, y=mpg$hwy, type="scatter", color=as.factor(mpg$cyl))
```

## Generate 3d scatterplot data
We will generate some random data for a 3 dimensional scatterplot.
```{r scatter3d_data}
set.seed(42)
tmp <- rnorm(150, mean=20, sd=4)
pres <- rnorm(150)
dtime <- 1:150
```

## Create 3d scatterplot
```{r scatter3d, warning=FALSE, message=FALSE}
plot_ly(x=tmp, y=pres, z=dtime, type="scatter3d", mode="markers", color=tmp)
```

## Plotly & ggplot2 (diamonds data)
```{r ggplot, warning=FALSE, message=FALSE}
plot_ly(ggplot2::diamonds, y = ~carat, color= ~cut, type = "box", 
        boxpoints = "all", jitter = 0.3, pointpos = -1.8)
```

## Conclusion
Plotly is a very useful package that can be used to create interactive graphs
with little efford. It is very effective tool for R markdown presentations or
reports.

